---
title: "R Notebook"
output: html_notebook
---


# US adults

1. Use participants' responses (participant level) to infer factor structure (group level).

[see primary analysis]

```{r}
loadings_us_adults <- efa_us_adults$loadings[] %>%
  data.frame() %>%
  rename_all(~ gsub("^.*_", "", .)) %>%
  rownames_to_column("capacity") %>%
  mutate(capacity = gsub(" \\[\\.\\.\\.\\]", "", capacity),
         capacity = gsub(" ", "_", capacity)) %>%
  column_to_rownames("capacity") %>%
  as.matrix() %>%
  # rescale to range from 0 to 1
  scales::rescale(to = c(0, 1), from = c(-1, 1))

head(loadings_us_adults)
```

2. Use factor structure (group level) in combination with responses (participant level) to generate factor scores (participant level).

```{r}
scores_us_adults <- efa_us_adults$scores[] %>% 
  # rescale to range from 0 to 1, using observed range of factor scores
  scales::rescale(to = c(0, 1))

head(scores_us_adults)
```

X. Use factor scores (participant level) to make binary decisions about attributions of body, heart, and mind (participant level level). [NEEDED?]

[not yet done]

3. Use factor scores [or X?] (participant level) in combination with factor loadings (group level) to to generate likelihood of each capacity (participant level).

```{r}
magic_us_adults <- magic_fun(loadings_us_adults, scores_us_adults) %>%
  data.frame()
```

4. Compare likelihood of each capacity (participant level) with actual responses (participant level) to assess consistency or violations with group-level factor structure.

```{r}
magic_sub_data_us_adults <- magic_us_adults - d_us_adults_w

magic_sub_data_us_adults <- magic_sub_data_us_adults %>%
  data.frame() %>%
  rownames_to_column("subj_id") %>%
  gather(capacity, diff, -subj_id) %>%
  mutate(capacity = gsub("_", " ", capacity),
         capacity = gsub("feel sick", "feel sick \\[\\.\\.\\.\\]", capacity))
```

```{r, fig.width = 4, fig.asp = 2}
magic_sub_data_us_adults %>%
  left_join(d_us_adults %>% distinct(subj_id, target)) %>%
  left_join(loadings_adults %>% 
              distinct(capacity, capacity_ord_us)) %>%
  ggplot(aes(x = capacity_ord_us, 
             y = subj_id, 
             fill = diff)) +
  facet_grid(rows = vars(target), 
             space = "free", scales = "free") +
  geom_tile() +
  scale_fill_distiller(type = "div") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "US adults",
       x = "Capacity", y = "Participant", fill = "Predicted - Actual")
```

```{r}
magic_sub_data_us_adults %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = mean_diff)) +
  geom_vline(xintercept = 0, lty = 2, color = "gray50") +
  geom_density() +
  labs(title = "US adults",
       x = "Mean Predicted - Actual", y = "Density")
```


# Ghana adults

1. Use participants' responses (participant level) to infer factor structure (group level).

[see primary analysis]

```{r}
loadings_gh_adults <- efa_gh_adults$loadings[] %>%
  data.frame() %>%
  rename_all(~ gsub("^.*_", "", .)) %>%
  rownames_to_column("capacity") %>%
  mutate(capacity = gsub(" \\[\\.\\.\\.\\]", "", capacity),
         capacity = gsub(" ", "_", capacity)) %>%
  column_to_rownames("capacity") %>%
  as.matrix() %>%
  # rescale to range from 0 to 1
  scales::rescale(to = c(0, 1), from = c(-1, 1))

head(loadings_gh_adults)
```

2. Use factor structure (group level) in combination with responses (participant level) to generate factor scores (participant level).

```{r}
scores_gh_adults <- efa_gh_adults$scores[] %>% 
  # rescale to range from 0 to 1, using observed range of factor scores
  scales::rescale(to = c(0, 1))

head(scores_gh_adults)
```

X. Use factor scores (participant level) to make binary decisions about attributions of body, heart, and mind (participant level level). [NEEDED?]

[not yet done]

3. Use factor scores [or X?] (participant level) in combination with factor loadings (group level) to to generate likelihood of each capacity (participant level).

```{r}
magic_gh_adults <- magic_fun(loadings_gh_adults, scores_gh_adults) %>%
  data.frame()
```

4. Compare likelihood of each capacity (participant level) with actual responses (participant level) to assess consistency or violations with group-level factor structure.

```{r}
magic_sub_data_gh_adults <- magic_gh_adults - d_gh_adults_w

magic_sub_data_gh_adults <- magic_sub_data_gh_adults %>%
  data.frame() %>%
  rownames_to_column("subj_id") %>%
  gather(capacity, diff, -subj_id) %>%
  mutate(capacity = gsub("_", " ", capacity),
         capacity = gsub("feel sick", "feel sick \\[\\.\\.\\.\\]", capacity))
```

```{r, fig.width = 4, fig.asp = 2}
magic_sub_data_gh_adults %>%
  left_join(d_gh_adults %>% distinct(subj_id, target)) %>%
  left_join(loadings_adults %>% 
              distinct(capacity, capacity_ord_gh)) %>%
  ggplot(aes(x = capacity_ord_gh, 
             y = subj_id, 
             fill = diff)) +
  facet_grid(rows = vars(target), 
             space = "free", scales = "free") +
  geom_tile() +
  scale_fill_distiller(type = "div") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Ghana adults",
       x = "Capacity", y = "Participant", fill = "Predicted - Actual")
```

```{r}
magic_sub_data_gh_adults %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = mean_diff)) +
  geom_vline(xintercept = 0, lty = 2, color = "gray50") +
  geom_density() +
  labs(title = "Ghana adults",
       x = "Mean Predicted - Actual", y = "Density")
```



# Thailand adults

1. Use participants' responses (participant level) to infer factor structure (group level).

[see primary analysis]

```{r}
loadings_th_adults <- efa_th_adults$loadings[] %>%
  data.frame() %>%
  rename_all(~ gsub("^.*_", "", .)) %>%
  rownames_to_column("capacity") %>%
  mutate(capacity = gsub(" \\[\\.\\.\\.\\]", "", capacity),
         capacity = gsub(" ", "_", capacity)) %>%
  column_to_rownames("capacity") %>%
  as.matrix() %>%
  # rescale to range from 0 to 1
  scales::rescale(to = c(0, 1), from = c(-1, 1))

head(loadings_th_adults)
```

2. Use factor structure (group level) in combination with responses (participant level) to generate factor scores (participant level).

```{r}
scores_th_adults <- efa_th_adults$scores[] %>% 
  # rescale to range from 0 to 1, using observed range of factor scores
  scales::rescale(to = c(0, 1))

head(scores_th_adults)
```

X. Use factor scores (participant level) to make binary decisions about attributions of body, heart, and mind (participant level level). [NEEDED?]

[not yet done]

3. Use factor scores [or X?] (participant level) in combination with factor loadings (group level) to to generate likelihood of each capacity (participant level).

```{r}
magic_th_adults <- magic_fun(loadings_th_adults, scores_th_adults) %>%
  data.frame()
```

4. Compare likelihood of each capacity (participant level) with actual responses (participant level) to assess consistency or violations with group-level factor structure.

```{r}
magic_sub_data_th_adults <- magic_th_adults - d_th_adults_w

magic_sub_data_th_adults <- magic_sub_data_th_adults %>%
  data.frame() %>%
  rownames_to_column("subj_id") %>%
  gather(capacity, diff, -subj_id) %>%
  mutate(capacity = gsub("_", " ", capacity),
         capacity = gsub("feel sick", "feel sick \\[\\.\\.\\.\\]", capacity))
```

```{r, fig.width = 4, fig.asp = 2}
magic_sub_data_th_adults %>%
  left_join(d_th_adults %>% distinct(subj_id, target)) %>%
  left_join(loadings_adults %>% 
              distinct(capacity, capacity_ord_th)) %>%
  ggplot(aes(x = capacity_ord_th, 
             y = subj_id, 
             fill = diff)) +
  facet_grid(rows = vars(target), 
             space = "free", scales = "free") +
  geom_tile() +
  scale_fill_distiller(type = "div") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Thailand adults",
       x = "Capacity", y = "Participant", fill = "Predicted - Actual")
```

```{r}
magic_sub_data_th_adults %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = mean_diff)) +
  geom_vline(xintercept = 0, lty = 2, color = "gray50") +
  geom_density() +
  labs(title = "Thailand adults",
       x = "Mean Predicted - Actual", y = "Density")
```


# China adults

1. Use participants' responses (participant level) to infer factor structure (group level).

[see primary analysis]

```{r}
loadings_ch_adults <- efa_ch_adults$loadings[] %>%
  data.frame() %>%
  rename_all(~ gsub("^.*_", "", .)) %>%
  rownames_to_column("capacity") %>%
  mutate(capacity = gsub(" \\[\\.\\.\\.\\]", "", capacity),
         capacity = gsub(" ", "_", capacity)) %>%
  column_to_rownames("capacity") %>%
  as.matrix() %>%
  # rescale to range from 0 to 1
  scales::rescale(to = c(0, 1), from = c(-1, 1))

head(loadings_ch_adults)
```

2. Use factor structure (group level) in combination with responses (participant level) to generate factor scores (participant level).

```{r}
scores_ch_adults <- efa_ch_adults$scores[] %>% 
  # rescale to range from 0 to 1, using observed range of factor scores
  scales::rescale(to = c(0, 1))

head(scores_ch_adults)
```

X. Use factor scores (participant level) to make binary decisions about attributions of body, heart, and mind (participant level level). [NEEDED?]

[not yet done]

3. Use factor scores [or X?] (participant level) in combination with factor loadings (group level) to to generate likelihood of each capacity (participant level).

```{r}
magic_ch_adults <- magic_fun(loadings_ch_adults, scores_ch_adults) %>%
  data.frame()
```

4. Compare likelihood of each capacity (participant level) with actual responses (participant level) to assess consistency or violations with group-level factor structure.

```{r}
magic_sub_data_ch_adults <- magic_ch_adults - d_ch_adults_w

magic_sub_data_ch_adults <- magic_sub_data_ch_adults %>%
  data.frame() %>%
  rownames_to_column("subj_id") %>%
  gather(capacity, diff, -subj_id) %>%
  mutate(capacity = gsub("_", " ", capacity),
         capacity = gsub("feel sick", "feel sick \\[\\.\\.\\.\\]", capacity))
```

```{r, fig.width = 4, fig.asp = 2}
magic_sub_data_ch_adults %>%
  left_join(d_ch_adults %>% distinct(subj_id, target)) %>%
  left_join(loadings_adults %>% 
              distinct(capacity, capacity_ord_ch)) %>%
  ggplot(aes(x = capacity_ord_ch, 
             y = subj_id, 
             fill = diff)) +
  facet_grid(rows = vars(target), 
             space = "free", scales = "free") +
  geom_tile() +
  scale_fill_distiller(type = "div") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "China adults",
       x = "Capacity", y = "Participant", fill = "Predicted - Actual")
```

```{r}
magic_sub_data_ch_adults %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = mean_diff)) +
  geom_vline(xintercept = 0, lty = 2, color = "gray50") +
  geom_density() +
  labs(title = "China adults",
       x = "Mean Predicted - Actual", y = "Density")
```


# Vanuatu adults

1. Use participants' responses (participant level) to infer factor structure (group level).

[see primary analysis]

```{r}
loadings_vt_adults <- efa_vt_adults$loadings[] %>%
  data.frame() %>%
  rename_all(~ gsub("^.*_", "", .)) %>%
  rownames_to_column("capacity") %>%
  mutate(capacity = gsub(" \\[\\.\\.\\.\\]", "", capacity),
         capacity = gsub(" ", "_", capacity)) %>%
  column_to_rownames("capacity") %>%
  as.matrix() %>%
  # rescale to range from 0 to 1
  scales::rescale(to = c(0, 1), from = c(-1, 1))

head(loadings_vt_adults)
```

2. Use factor structure (group level) in combination with responses (participant level) to generate factor scores (participant level).

```{r}
scores_vt_adults <- efa_vt_adults$scores[] %>% 
  # rescale to range from 0 to 1, using observed range of factor scores
  scales::rescale(to = c(0, 1))

head(scores_vt_adults)
```

X. Use factor scores (participant level) to make binary decisions about attributions of body, heart, and mind (participant level level). [NEEDED?]

[not yet done]

3. Use factor scores [or X?] (participant level) in combination with factor loadings (group level) to to generate likelihood of each capacity (participant level).

```{r}
magic_vt_adults <- magic_fun(loadings_vt_adults, scores_vt_adults) %>%
  data.frame()
```

4. Compare likelihood of each capacity (participant level) with actual responses (participant level) to assess consistency or violations with group-level factor structure.

```{r}
magic_sub_data_vt_adults <- magic_vt_adults - d_vt_adults_w

magic_sub_data_vt_adults <- magic_sub_data_vt_adults %>%
  data.frame() %>%
  rownames_to_column("subj_id") %>%
  gather(capacity, diff, -subj_id) %>%
  mutate(capacity = gsub("_", " ", capacity),
         capacity = gsub("feel sick", "feel sick \\[\\.\\.\\.\\]", capacity))
```

```{r, fig.width = 4, fig.asp = 2}
magic_sub_data_vt_adults %>%
  left_join(d_vt_adults %>% distinct(subj_id, target)) %>%
  left_join(loadings_adults %>% 
              distinct(capacity, capacity_ord_vt)) %>%
  ggplot(aes(x = capacity_ord_vt, 
             y = subj_id, 
             fill = diff)) +
  facet_grid(rows = vars(target), 
             space = "free", scales = "free") +
  geom_tile() +
  scale_fill_distiller(type = "div") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Vanuatu adults",
       x = "Capacity", y = "Participant", fill = "Predicted - Actual")
```

```{r}
magic_sub_data_vt_adults %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = mean_diff)) +
  geom_vline(xintercept = 0, lty = 2, color = "gray50") +
  geom_density() +
  labs(title = "Vanuatu adults",
       x = "Mean Predicted - Actual", y = "Density")
```

# Comparison

```{r}
bind_rows(magic_sub_data_us_adults,
          magic_sub_data_gh_adults,
          magic_sub_data_th_adults,
          magic_sub_data_ch_adults,
          magic_sub_data_vt_adults) %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  mutate(country = gsub("_.*$", "", subj_id),
         country = factor(country,
                          levels = c("us", "gh", "th", "ch", "vt"),
                          labels = levels_country),
         target = gsub("^.*_", "", subj_id),
         target = factor(target, levels = levels_target_univ)) %>%
  ggplot(aes(x = country, y = mean_diff)) +
  geom_hline(yintercept = 0, lty = 2, color = "gray50") +
  geom_jitter(aes(color = country), height = 0, alpha = 0.5, show.legend = F) +
  geom_pointrange(data = . %>%
                    distinct(country, subj_id, mean_diff) %>%
                    group_by(country) %>%
                    multi_boot_standard(col = "mean_diff"),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black") +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "All adults",
       x = "Country", y = "Mean Predicted - Actual")
```
```{r}
bind_rows(magic_sub_data_us_adults,
          magic_sub_data_gh_adults,
          magic_sub_data_th_adults,
          magic_sub_data_ch_adults,
          magic_sub_data_vt_adults) %>%
  group_by(subj_id) %>%
  summarise(mean_diff = mean(diff, na.rm = T)) %>%
  ungroup() %>%
  mutate(country = gsub("_.*$", "", subj_id),
         country = factor(country,
                          levels = c("us", "gh", "th", "ch", "vt"),
                          labels = levels_country),
         target = gsub("^.*_", "", subj_id),
         target = factor(target, levels = levels_target_univ),
         abs_mean_diff = abs(mean_diff)) %>%
  ggplot(aes(x = country, y = abs_mean_diff)) +
  geom_hline(yintercept = 0, lty = 2, color = "gray50") +
  geom_jitter(aes(color = country), height = 0, alpha = 0.5, show.legend = F) +
  geom_pointrange(data = . %>%
                    distinct(country, subj_id, abs_mean_diff) %>%
                    group_by(country) %>%
                    multi_boot_standard(col = "abs_mean_diff"),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black") +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "All adults",
       x = "Country", y = "ABSOLUTE Mean Predicted - Actual")
```
